Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-17 ms.qmd
Fixed lnCVR figure

### *Sensitivity Analyses*
### *Publication Bias*

@@

```{r}
#| label: fig-fig8
#| fig-align: center
#| fig-cap: Bubble plot environment lnRR for wild populations by habitat

@@

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))

@@

```{r}
#| label: fig-fig9
#| fig-align: center
#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
 col <- c("#0871B9", "#F3B40D", "#1BB908")
p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))

p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))

p91.2 <- p9.1 / p9.2
p91.2
ggsave(p91.2, filename = "./output/figures/fig9.png")
```

>>>>

### *Publication Bias*

We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) and publication year [@Nakagawa2021-gy]. Funnel plot asymetry may suggest a form of publication called a 'file-drawer' effect whereby low-powered studies are less likely to be published. However, asymetry can also result form high hetereogenity. As such, testing (and correcting) for publication bias using a meta-regression approach can attempt to counteract bias that maybe driven by high effect hetereogneity. In addition, a second form of publication bias, time-lag bias, is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2022-qw].

@@

```{r}
#| label: fig-fig8
#| fig-align: center
#| fig-cap: Bubble plot environment $lnRR_{Q_{10}}$ for wild populations by habitat.

@@

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))

@@

```{r}
#| label: fig-fig9
#| fig-align: center
#| fig-cap: Bubble plot environment $lnCVR_{Q_{10}}$ for wild populations by habitat.

size_axis = 18
# CV
dat_text <- data.frame(label = c(text(slope_f_4.9), text(slope_m_4.9), text(slope_t_4.9)),
                      label2 = c(text(slope_f_4.9, b = FALSE), text(slope_m_4.9,b = FALSE), text(slope_t_4.9,b = FALSE)),
                      p = c(p_text(slope_f_4.9), p_text(slope_m_4.9), p_text(slope_t_4.9)),
                      title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(1.2, 3),
                      y = rep(-4, 3))

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnCVRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text, aes(x = x, y = y-1, label = label2), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y-2, label = p), size = 5) +
geom_text(data = dat_text, aes(x = x, y = y+10, label = title, size = 5)) + 
theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))

  # ACF
dat_text2 <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
                      condition = c("f", "m", "t"),
                      x = rep(-2.8, 3),
                      y = rep(-4, 3))

p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnCVRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text2, aes(x = x, y = y-0.6, label = label2), size = 5) +
geom_text(data = dat_text2, aes(x = x, y = y-1.2, label = p), size = 5) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))

ggsave(p9.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig9.png")

  p9.1.2 <- image_read("./output/figures/fig8.png")
  p9.1.2 
```
